---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# hakedataUSA

<!-- badges: start -->
<!-- badges: end -->

The goal of {hakedataUSA} is to provide code to extract and workup the U.S. data
for the assessment of Pacific Hake.

## Instructions

1. First, you must update `data-raw/quotas.csv` to include the sector-specific
   quotas. These values are used when processing the data, mainly for the
   creation of figures. Then, from within R, source `data-raw/quotas.R` and the
   internal data object will be updated and ready for use. Commit both
  `data-raw/quotas.csv` and `data-quotas.rda` to the repository and push.
1. Next, load the package. This can be accomplished through GitHub (first
   chunk) or using a local clone (second chunk).
   ```{r installation-github}
chooseCRANmirror(ind = 1)
# install.packages("pak")
pak::pak("pacific-hake/hakedataUSA")
library(hakedataUSA)
   ```
   ```{r installation-local}
chooseCRANmirror(ind = 1)
stopifnot(basename(getwd()) == "hakedataUSA")
devtools::load_all()
   ```
1. The path to where all of the raw output will be saved is stored in an 
   internal function, i.e., `hakedata_wd()`. Try it out, see if it works for 
   you. If it does not work, then you will need to alter the function, which is 
   stored in `R/hakedata-R`. The function should result in a path ending with 
   `data-tables` inside of your cloned version of
   [pacific-hake/hake-assessment][hake-assessment].
1. The remainder of the code will pull from the data bases and set up the input
   files.
```{r execute}
pull_database()
process_database()

write_bridging(
  dir_input = fs::path(dirname(hakedata_wd()), "models", "2022.01.10_base"),
  dir_output = fs::path(dirname(hakedata_wd()), "models", "2023", "01-version", "02-bridging-models")
)
```

## Issues

Please contact kelli.johnson@noaa.gov if there are issues with the code.
Note that the databases will only be accessible to U.S. members of the JTC.

[hake-assessment]: www.github.com/pacific-hake/hake-assessment
