---
title: "Summary of bycatch in U.S. At-Sea sector"
author: "Kelli F. Johnson"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2
---

**Please do NOT share this document** given that information summarized in
at least one of the included figures shows summary statistics for groups
containing less than three vessels.

Data from NORPAC is used to calculate monthly, fishery-specific bycatch rates
for each year (Figure \@ref(fig:catch-rates)). These are used to extrapolate
the amount of bycatch there might have been in unsampled tows of Pacific Hake.
The hypothesized amount of bycatch is then subtracted from the total weight of
the unsampled tow to generate a total weight of Pacific Hake.

```{r set-up, eval = TRUE, echo = FALSE, error = FALSE, warning = FALSE, message = FALSE}
library(dplyr)
library(devtools)
load_all()
options(scipen = 999)
knitr::opts_chunk$set(
  echo = FALSE, results = "hide", cache = TRUE,
  message = FALSE, error = FALSE, warning = FALSE
)
load("../hake-assessment/data/extractedData/norpac_catch.Rdat")
species <- 206
current_year <- as.numeric(format(Sys.Date(), "%Y")) - 1

ncatch_formatted <- ncatch %>%
  dplyr::mutate(
    Date = f_date(RETRIEVAL_DATE, format = "%Y-%m-%d"),
    month = f_date(RETRIEVAL_DATE, format = "%m"),
    Month = f_date(RETRIEVAL_DATE, format = "%b", factor = TRUE),
    year = f_date(RETRIEVAL_DATE, "%Y"),
    # Create catch rate in mt/hr
    crate = EXTRAPOLATED_WEIGHT / 1000 / HRS,
    FISHING_DEPTH_M = FISHING_DEPTH_FATHOMS * fathom_to_meter,
    BOTTOM_DEPTH_M = BOTTOM_DEPTH_FATHOMS * fathom_to_meter,
    vesseltype = f_vessel_type(VESSEL_TYPE),
    Sector = "DomesticAtSea",
    sampled = ifelse(is.na(HAUL_SAMPLED_BY) | HAUL_SAMPLED_BY == 0, 0, 1),
    # Unsampled hauls will have a SPECIES == NA and EXTRAPOLATED_WEIGHT == NA
    SPECIES = ifelse(sampled == 0, species, SPECIES),
    OFFICIAL_TOTAL_CATCHkg = OFFICIAL_TOTAL_CATCH * 1000,
    # ByCatch (kg)
    ByCatch = OFFICIAL_TOTAL_CATCHkg - EXTRAPOLATED_WEIGHT
  )

entries_dont_match <- ncatch_formatted %>%
  dplyr::group_by(VESSEL, Date, HAUL, year, month, vesseltype) %>%
  dplyr::summarize(
    sum = sum(EXTRAPOLATED_WEIGHT),
    total = unique(OFFICIAL_TOTAL_CATCH) * 1000,
    diff = total - sum
  ) %>%
  dplyr::filter(abs(diff) > 0.1)

catch_rates <- ncatch_formatted %>%
  dplyr::filter(
    SPECIES == species,
    sampled == 1
  ) %>%
  dplyr::group_by(vesseltype, VESSEL, HAUL, HAUL_DATE, CRUISE, PERMIT) %>%
  dplyr::mutate(
    bycatch_kg = OFFICIAL_TOTAL_CATCH * 1000 - EXTRAPOLATED_WEIGHT
  ) %>%
  dplyr::group_by(year, month, vesseltype) %>%
  dplyr::summarize(
    bycatch_kg = sum(bycatch_kg),
    OFFICIAL_TOTAL_CATCHkg = sum(OFFICIAL_TOTAL_CATCH) * 1000,
    bycatchrate = bycatch_kg / OFFICIAL_TOTAL_CATCHkg
  ) %>%
  dplyr::full_join(
    ncatch_formatted %>%
      dplyr::filter(sampled == 0, OFFICIAL_TOTAL_CATCH > 0) %>%
      dplyr::group_by(year, month, vesseltype) %>%
      dplyr::summarize(
        n = n(),
        unsampled_mt = sum(OFFICIAL_TOTAL_CATCH)
      ),
    by = c("year", "month", "vesseltype")
  )

ncatch_bycatch <- dplyr::full_join(
  ncatch_formatted %>%
    dplyr::filter(SPECIES == species, sampled == 1) %>%
    dplyr::group_by(year, month, vesseltype) %>%
    dplyr::summarize(
      catch_sampled = sum(EXTRAPOLATED_WEIGHT, na.rm = TRUE),
      catch_bycatch = sum(OFFICIAL_TOTAL_CATCH * 1000 - EXTRAPOLATED_WEIGHT, na.rm = TRUE)
    ),
  ncatch_formatted %>%
    dplyr::group_by(year, month, vesseltype) %>%
    dplyr::filter(SPECIES != species, sampled == 1) %>%
    dplyr::summarize(
      catch_bycatch_other = sum(EXTRAPOLATED_WEIGHT)
    ),
  by = c("year", "month", "vesseltype")
) %>%
  dplyr::mutate(
    bycatchrate = catch_bycatch / catch_sampled,
    test = catch_bycatch - catch_bycatch_other,
    sampled = 0
  )
test <- dplyr::left_join(
  ncatch_formatted,
  ncatch_bycatch,
  by = c("year", "month", "vesseltype", "sampled")
)
```

In `r current_year`, the total landings (mt) brought on board and **NOT**
sampled was estimated to sum to
`r dplyr::filter(catch_rates, year == current_year, vesseltype == "CP") %>% dplyr::pull(unsampled_mt) %>% sum(na.rm = TRUE)` and
`r dplyr::filter(catch_rates, year == current_year, vesseltype == "MS") %>% dplyr::pull(unsampled_mt) %>% sum(na.rm = TRUE)` (mt)
for Catcher-Processors and Motherships, respectively. The total landings of
Pacific Hake in the Catcher-Processor fleet for `r current_year` was estimated
to be 126,247.03 (mt). The total landings of Pacific Hake in the Mothership
fleet for `r current_year` was estimated to be 59,152.31 (mt). Which, makes for
`r round(126247.03/126287*100, 2)` and `r round(59152.31/89144*100, 2)`
percent attainment, respectively. These estimates are known to be different
than the information provided in the [Commercial At-Sea Pacific Whiting Fishery
and Shoreside Targeted Whiting Fishery Summary
](https://reports.psmfc.org/pacfin/f?p=501:202::INITIAL:YES:::).
Approximately, 126,246.74 and 59,157.13 (mt) were landed in by Catcher-
Processors and Motherships, respectively.

I found that the estimates of bycatch rates changed depending on how landing of
non-target species is calculated. That is, adding `EXTRAPOLATED_WEIGHT` of
non-target species is not the same as subtracting `EXTRAPOLATED_WEIGHT` of
Pacific Hake from the `OFFICIAL_TOTAL_CATCH` after accounting for differences
in units. There are many records where these two numbers do not add up after
accounting for what I consider to be rounding errors, i.e., differences of
less than 0.1. Beyond not knowing exactly how to calculate the total amount
of bycatch in sampled tows, there will always be differences between
numbers reported in PacFIN and those reported in the stock assessment
because the JTC is using monthly-specific bycatch rates for each vessel type
instead of bycatch rates from like tows that are calculated in season.

The goal is to best estimate the amount of Pacific Hake that was removed
from U.S. waters and I am uncertain which method accomplishes that. Though
it is clear that that amount of bycatch differs by fishery, month, and
year (Figures \@ref(fig:catch-rates) and \@ref(fig:total-bycatch)).

```{r catch-rates, fig.cap = "\\label{fig:catch-rates}Bycatch (kg) / total catch (kg) by month (x axis), year (panel), and fishery (color). Size of the points indicates the amount of unsampled landings (mt)."}
ggplot2::ggplot(
    data = catch_rates %>% dplyr::filter(vesseltype != 3),
    ggplot2::aes(x = month, y = bycatchrate, group = vesseltype, colour = vesseltype)
) +
  ggplot2::geom_point(alpha = .5, ggplot2::aes(size = unsampled_mt)) +
  ggplot2::geom_line() +
  ggplot2::facet_wrap("year", scales = "fixed") +
  ggplot2::theme_bw() +
  ggplot2::ylab("bycatch (kg) / total catch (kg)")
```

```{r total-bycatch, fig.cap = "\\label{fig:total-bycatch}Weight (kg) of bycatch by year (x axis), month (color), and vessel type (panel) in the at-sea fishery."}
ncatch_formatted %>%
  dplyr::filter(SPECIES != species, VESSEL_TYPE != 3, !is.na(EXTRAPOLATED_WEIGHT)) %>%
  dplyr::group_by(year, Month = factor(month), vesseltype) %>%
  dplyr::summarize(EXTRAPOLATED_WEIGHT = sum(EXTRAPOLATED_WEIGHT)) %>%
  ggplot2::ggplot(ggplot2::aes(
    x = year,
    y = EXTRAPOLATED_WEIGHT,
    colour = Month,
    group = Month
  )) +
  ggplot2::geom_line() +
  ggplot2::geom_point() +
  ggplot2::facet_grid(. ~ vesseltype, scales = "fixed") +
  ggplot2::ylab("Extrapolated weight (kg) of sampled bycatch") +
  ggplot2::theme_bw()
```
